Incremental Faint Object Detection in Multi-Epoch Observations

### 2016-11-04 jetsam.tex
Move some redundant material from Summary

>>>>

%%%%%%%% From summary:

explored new approaches to processing a series of exposures with special focus on the faintest sources, where most of the new discoveries are expected.
%
We found that one can recover sources just by collecting a number of detections above even a low threshold with the same probability as if the sources were extracted from coadded images. Consequently we can develop incremental algorithms that crossmatch the detections and weed out the noise on the fly from a master source catalog.
